Differential invariant signatures for planar Lie group transformations of images

### 2020-07-28 paper/newpaper.tex
Changes from July Kapiti meetup

% REQUIRED
\begin{AMS}
\end{AMS}

@@

\begin{align}
I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) \\
I_4 &= f_x^2 f_{xx} - 2 f_x f_y f_{xy} + f_y^2 f_{yy} 
\end{align}

\todo[inline]{Richard: Check if the summation and negation (!) of I2 and I4
are actually invariants. Then we can write this bit. I3 is Robert's one.}
%However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$. Which is the product of 2 invariants in Einstein summation, but a pain in the arse any other way. But I can't see how else to get $f_{ii}$!

@@

\todo[inline]{Number of derivatives}
\item[inline]{Noise; integral invariants, Fourier}
\todo[inline]{Is there a general theory - syzygy??}

>>>>

% REQUIRED
\begin{AMS}

\end{AMS}

@@

\begin{align}
I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) \\
I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} 
\end{align}

@@

\todo[inline]{Number of derivatives}
\todo[inline]{Noise; integral invariants, Fourier}
\todo[inline]{Is there a general theory - syzygy??}
